---
title: "1-setting-up-demo-doc"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading, setting up 

Let's first load the {dataedu} package and the {tidyverse} suite of packages.

```{r}
library(dataedu)
library(tidyverse)
```

If you saw some messages, success!

Here is the data set we will use:

```{r}
sci_mo_processed
```

# An introduction to ggplot2

## Bar chart

```{r}

```

## Scatterplot

```{r}

```

#3 Adding a line of best fit

```{r}

```

# Exploring data

## Printing

```{r}

```

## Viewing data

```{r}

```

## Counting

```{r}

```

# Beyond the basics of ggplot2

## Colors

```{r}

```

# Theming

```{r}

```

# Saving plots

```{r}

```

# Creating a GIF (leap)

```{r}

```







# Demo doc (part 2): Try it out!

`geom_jitter()` is exactly like geom_point, but with a small amount of x- and y-axis random noise added.

```{r}
ggplot(gss_cat, aes(x = age, y = tvhours)) +
  geom_jitter()
```

**Try it out!**

Can you add a line representing the linear relationship between the two varibles? Add another layer using a `geom_` function.


```{r}
# hint: check out how a line was added in the presentation? 

ggplot(gss_cat, aes(x = age, y = tvhours)) +
  geom_jitter() +
  geom_
```

Let's try a different theme.

```{r}
ggplot(gss_cat, aes(x = age, y = tvhours)) +
  geom_jitter() +
  theme_bw()
```

**Try it out!**

Can you add a different theme? Start typing `theme_` and see what shows up! Be sure to run the code to see the results!

```{r}
ggplot(gss_cat, aes(x = age, y = tvhours)) +
  geom_jitter() +
  theme_
```

Does the relationship look to be different by year?

```{r}
ggplot(gss_cat, aes(x = age, y = tvhours)) +
  geom_jitter() +
  facet_wrap(~year)
```

**Try it out!**

Can you add lines of best fit to the above plots?

```{r}
ggplot(gss_cat, aes(x = age, y = tvhours)) +
  geom_jitter() +
  geom_
  facet_wrap(~year)
```

