---
title: "1-setting-up-demo-doc"
author: ""
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading, setting up 

Let's first load the {dataedu} package and the {tidyverse} suite of packages.

```{r}
library(dataedu)
library(tidyverse)
library(ggthemes)
```

Here is the data set we will use (again):

```{r}
sci_mo_processed
```

# An introduction to ggplot2

## Bar chart

Let's start by counting the number of students in each course.

```{r}
sci_mo_processed %>% 
  count(course_id)
```
So far, so good. But, how can we visualize these? Let's try a bar chart:

```{r}
sci_mo_processed %>% 
  count(course_id) %>% 
  ggplot(aes(x = course_id, y = n)) +
  geom_col()
```
Well, that worked - sort of! How can we improve this plot? We'll do two things:

- Flip the coordinates, so we can read the labels more easily
- Arrange the bars (columns) by the number of students in each course

```{r}
sci_mo_processed %>% 
  count(course_id) %>% 
  ggplot(aes(x = reorder(course_id, n), y = n)) +
  geom_col() +
  coord_flip()
```

Let's color the bars by subject to see if patterns in course size can be identified.

```{r}
sci_mo_processed %>% 
  count(course_id, subject) %>% 
  ggplot(aes(x = reorder(course_id, n), y = n, fill = subject)) +
  geom_col() +
  coord_flip()
```

**Try it out!**

Instead of course_id, can you visualize another variable? Try to replace course_id below with subject.

```{r}
sci_mo_processed %>% 
  count(course_id) %>% 
  ggplot(aes(x = course_id, y = n)) +
  geom_col()
```
Can you reorder the bars (columns) above, using the same reordering we used in the first plot?

## Scatterplot

Let's start with the plot we looked at earlier:

```{r}
sci_mo_processed %>% 
  ggplot(aes(x = percentage_earned, y = TimeSpent)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw() +
  facet_wrap(~subject)
```

** Try it out!**

What if we wanted a different theme?

Replace theme_bw() with one of the following:

- theme_tufte()
- theme_clean()
- theme_fivethirtyeight()

```{r}
sci_mo_processed %>% 
  ggplot(aes(x = percentage_earned, y = TimeSpent)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw() +
  facet_wrap(~subject)
```

# Exploring data

Let's back up and spend a bit of time exploring data.

## Printing

```{r}
sci_mo_processed
```

## Viewing data

We can also use the View() function to view the data in a spreadsheet-like way:

```{r, eval = FALSE}
View(sci_mo_processed)
```

## Counting

Counting is a surprisingly useful data analysis technique. Let's start with 
counting one variable:

```{r}
sci_mo_processed %>% 
  count(student_id)
```
What do you notice? What do you wonder?

**Try it out!**

Replace student_id with Gradebook_Item, and then run the code below:

```{r}
sci_mo_processed %>% 
  count(student_id)
```

# Beyond the basics of ggplot2

## Colors

Colors can easily be changed; here are some options: http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf

```{r}
sci_mo_processed %>% 
  count(course_id) %>% 
  ggplot(aes(x = reorder(course_id, n), y = n)) +
  geom_col(fill = "darkslateblue") +
  coord_flip()
```

**Try it out!**

Can you replace darkslateblue with a different color?

```{r}
sci_mo_processed %>% 
  count(course_id) %>% 
  ggplot(aes(x = reorder(course_id, n), y = n)) +
  geom_col(fill = "darkslateblue") +
  coord_flip()
```

# Saving plots

**Try it out!**

Plots can be saved easily; by default, this function will save your last plot

```{r}
ggsave("my-courses-plot.png", width = 6, height = 4)
```

# Rendering this document to a PDF report 

- add your name as the author at the very top of this document
- click "Knit" and check out the result!

# Creating a GIF (leap)

```{r, eval = FALSE}
library(gganimate)

sci_mo_processed %>% 
  ggplot(aes(x = percentage_earned, y = TimeSpent)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw() +
  transition_states(subject) +
  labs(title = 'Subject: {subject}')
```

You can save this with:

```{r, eval = FALSE}
anim_save("mygif.gif", width = 500, height = 500)
```

For what other variables could you "animate" a plot? Try replacing subject below.

```{r, eval = FALSE}
library(gganimate)

sci_mo_processed %>% 
  ggplot(aes(x = percentage_earned, y = TimeSpent)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw() +
  transition_states(subject) +
  labs(title = 'Subject: {subject}')
```

```{r, eval = FALSE}
anim_save("mysecondgif.gif", width = 500, height = 500)
```