---
title: "1-setting-up-demo-doc"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's first load the {dataedu} package and the {tidyverse} suite of packages.

```{r}
library(dataedu)
library(tidyverse)
```

If you saw some messages, success!

Here is the data set we will use:

```{r}
sci_mo_processed
```

# Demo doc (part 3): Try it out!

Let's run a regression.

```{r}
m1 <- lm(tvhours ~ age, data = gss_cat)
summary(m1)
```

Character strings and factors are automatically dummy-coded by `lm()`:

```{r}
m2 <- lm(tvhours ~ marital, data = gss_cat)
summary(m2)
```

**Try it out!**

Can you add another variable to the model? If you need to check what variables are in `gss_cat`, print that object to the console. What do you notice about the output?

```{r}
m3 <- lm(tvhours ~ age + , data = gss_cat)
summary(m3)
```


# Mutate

Let's create a new variable for those 60 years of age or older.

```{r}
gss_cat %>% 
  mutate(potential_senior = if_else(age >= 63.5, 1, 0),
         super_senior = if_else(potential_senior == 1 & tvhours < 2, 1, 0)) %>% 
  count(potential_senior, super_senior)
```

Let's save the results back to `gss_cat` and make sure that it worked.

```{r}
gss_cat <- gss_cat %>% 
  mutate(potential_senior = ifelse(age >= 63.5, TRUE, FALSE))
```

Adding another variable for folks who are middle-aged.

```{r}
gss_cat <- gss_cat %>% 
  mutate(middle_aged = ifelse(age >= 30 & age <= 40, "yes", "no"))
```

**Try it out!**

Can you create a new variable based upon either the *year* or *tvhours* variable using `if_else()`? 

```{r}
gss_cat %>% 
  mutate()
```

Then, save the results back to `gss_cat` (check out the code two chunks above for an example!).

```{r}
gss_cat %>% 
  mutate()
```