---
title: "1-setting-up-demo-doc"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's first load the {tidyverse} suite of packages as well as the {corrr} package.

```{r}
library(tidyverse)
```

If you saw some messages, success!

# Reading in an Excel file

Here, we will read in a dataset in Excel.

Click in the file ngsschatxlsx and then click Import Dataset.

Copy and paste that code here (below)!

```{r}

```

# Inspecting the data

```{r}
ngsschat
```

# Viewing the data (if you haven't already)

```{r}
View(ngsschat)
```

# Correlations

```{r}
ngsschat %>% 
  select(know_framework, know_ngss, confidence_ngss) %>% 
  corrr()
```

# `lm()`

```{r}
m1 <- lm(confidence_ngss ~ age_range, data = ngsschat)
summary(m1)
```

**Try it out!** 

What other variable can you add? Separate variables with a plus sign:

```{r}
m2 <- lm(confidence_ngss ~ age_range + , data = ngsschat)
summary(m2)
```

# Creating a new variable

```{r}
ngsschat <- ngsschat %>% 
  mutate(sum_self_reports = (know_framework + know_ngss + confidence_ngss) / 3)
```

# Writing data

You've read data; now let's consider writing data.

Let's imagine that we created a new dataset and want to save it.

To write data, I recommend write_csv():

```{r}
write_csv(ngsschat, "ngsschat_new.csv")
```

# Running a multi-level model (leap)

```{r}
library(lme4)

multilevel_m1 <- lm(FinalGradeCEMS ~ TimeSpent + int + subject + (1|course_id), data = sci_mo_processed)
summary(multilevel_m1)
```

What do you notice about the output?

