---
title: "1-setting-up-demo-doc"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's first load the {dataedu} package adn the {tidyverse} suite of packages.

```{r}
library(dataedu)
library(tidyverse)
```

If you saw some messages, success!

Here is the data set we will use:

```{r}
sci_mo_processed
```

# Demo doc (part 1): Try it out!

# Select

Let's select only a few variables.

```{r}
gss_cat %>% 
  select(year, tvhours)

gss_cat %>% 
  select(year, marital, tvhours)
```

**Try it out!**

Now, select three *different* variables, and run the code chunk to view the result.

```{r}
gss_cat %>% 
  select()
```

# Filter

```{r}
gss_cat %>% 
  filter(age > 60)
```

**Try it out!**

Filter to include only those individuals who watch a lot of TV - more than 10 hours per *day*!

Be sure to run the result to see whether it did what you think it should do!

```{r}
gss_cat %>% 
  
```

# Mutate

Let's create a new variable for those 60 years of age or older.

```{r}
gss_cat %>% 
  mutate(potential_senior = if_else(age >= 63.5, 1, 0),
         super_senior = if_else(potential_senior == 1 & tvhours < 2, 1, 0)) %>% 
  count(potential_senior, super_senior)
```

Let's save the results back to `gss_cat` and make sure that it worked.

```{r}
gss_cat <- gss_cat %>% 
  mutate(potential_senior = ifelse(age >= 63.5, TRUE, FALSE))
```

Adding another variable for folks who are middle-aged.

```{r}
gss_cat <- gss_cat %>% 
  mutate(middle_aged = ifelse(age >= 30 & age <= 40, "yes", "no"))
```

**Try it out!**

Can you create a new variable based upon either the *year* or *tvhours* variable using `if_else()`? 

```{r}
gss_cat %>% 
  mutate()
```

Then, save the results back to `gss_cat` (check out the code two chunks above for an example!).

```{r}
gss_cat %>% 
  mutate()
```