---
title: "1-setting-up-demo-doc"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading, setting up 

Let's first load the {dataedu} package adn the {tidyverse} suite of packages.

```{r}
library(dataedu)
library(tidyverse)

print("It worked!")
```

If you saw some messages, success!

Here is the data set we will use:

```{r}
sci_mo_processed
```

# Selecting variables

Let's select only a few variables.

```{r}
gss_cat %>% 
  select(year, tvhours)

gss_cat %>% 
  select(year, marital, tvhours)
```

**Try it out!**

Now, select three *different* variables, and run the code chunk to view the result.

```{r}
gss_cat %>% 
  select()
```

# Filtering variables

```{r}
gss_cat %>% 
  filter(age > 60)
```

**Try it out!**

Filter to include only those individuals who watch a lot of TV - more than 10 hours per *day*!

Be sure to run the result to see whether it did what you think it should do!

```{r}
gss_cat %>% 
  filter()
```

# Creating a plot (with ggplot2)

```{r}

```

**Try it out!**

```{r}

```

---

# Rendering this document to a PDF report 

- change the name at the very top of this document
- click "Knit"
- check out the result!

# Visualizing a larger dataset (leap)

```{r}

```