---
title: "Part 3: Modeling and Preparing Data"
subtitle: "Southern Wesleyan University, EdD Residency"
author: "Joshua M. Rosenberg, Ph.D, Assistant Professor, University of Tennessee, Knoxville"
date: "June 30, 2020"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

library(knitr)
library(tidyverse)
library(xaringan)
library(dataedu)

joro_years <- round(as.numeric(difftime(as.Date(Sys.Date()), Sys.getenv("joro_bday"), unit="weeks"))/52.25, 1)
```

class: inverse, center, middle

# Welcome back!

---

class: inverse, center, middle

# *Big idea*: Linear regression models are a general-purpose tool for analyzing data.

---

# Homebase

*These will appear in every presentation throughout the day today*

**All materials here:**
https://github.com/jrosen48/swu-data-sci

**RStudio Cloud**
https://rstudio.cloud/project/1427304

**Ask questions on Google Docs:**
https://docs.google.com/document/d/1zB3IilyuU0khd10DWQNn44peOkVNI-OLyxRW6WFW5Qw/edit

**Ask questions in Zoom chat!**

---

# Agenda

### Part 1: Getting up and running
### Part 2: Visualizing and exploring data
### *Part 3: Modeling and understanding data*
### Part 4: Doing more with data science

---

class: inverse, center, middle

# Regression

---

# Linear (regression) models

- Think about a linear (regression) model as a way to answer the question: *What is related to some outcome or result I care about?*
- *Dependent variable*: An outcome or result
- *Independent variable*: The thing(s) that relate to the outcome or result you crae about
- Sometimes, a regression with a single dependent variable and a single independent variable is called a single regression, and one with more than one independent variable is called a multiple regression

---

# Single regression example

```{r}
m1 <- lm(FinalGradeCEMS ~ TimeSpent, data = sci_mo_processed)
summary(m1)
```

---

# Multiple regression example

Note: int refers to students' interest

```{r}
m2 <- lm(FinalGradeCEMS ~ TimeSpent + int, data = sci_mo_processed)
summary(m2)
```

---

# Multiple regression example

Dummy-coding is a powerful (but easy in R ) technique; recall
that subject is a group---a factor

```{r, eval = FALSE}
m3 <- lm(FinalGradeCEMS ~ TimeSpent + int + subject, data = sci_mo_processed)
summary(m3)
```

---

class: inverse, center, middle

# Try it out! Linear models

*Let's hop over to the demo doc for part 3!*

- `lm()` (for linear model)
- reading and (especially) writing data
- multi-level models (leap)

---

# *Discuss in groups!*

- What challenges did you face?
- What successes did you face?
- What questions do you still have?

---

class: inverse, center, middle

# *Big idea*: Linear regression models are a general-purpose tool for analyzing data.

---

class: inverse, center, middle

# *Next*: Text analysis and beyond